---
title: "Tidy"
author: "JJayes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r}
library(tidyverse)
```


```{r}
df <- read_rds(here::here("data", "chocolate-bar-ratings.rds"))
```

### What does our data look like?

```{r}
df %>% skimr::skim()
```

Some things that we might want to do to make the analysis easier

- Locations into a standard format
- Change the ingredients from a character vector into a number and some some dummy variables

### Locations

```{r}
library(countrycode)

df <- df %>% 
  mutate(company_location_code = countrycode(company_location, "country.name", "iso3c"))

df <- df %>% 
  mutate(country_of_bean_origin_code = countrycode(country_of_bean_origin, "country.name", "iso3c"))
```

We are given warnings about Amsterdam, Scotland and Wales. We can use a `case_when` statement if we want. I'll come back to this.

### Ingredients

```{r}
df <- df %>% 
  separate(ingredients, c("n_ingredients", "ingredients"), "-") %>% 
  mutate(n_ingredients = parse_number(n_ingredients),
         ingredients = str_squish(ingredients))

df %>% 
  count(n_ingredients)
```

Most bars have 3 ingredients. What are they?

```{r}
df %>% 
  count(ingredients, sort = T)
```

What do these things mean? We will have to look back at the website!

B = Beans, S = Sugar, S* = Sweetener other than white cane or beet sugar, C = Cocoa Butter, V = Vanilla, L = Lecithin, Sa = Salt

```{r}
str <- "B = Beans, S = Sugar, S* = Sweetener other than white cane or beet sugar, C = Cocoa Butter, V = Vanilla, L = Lecithin, Sa = Salt"

str <- str %>% 
  as_tibble() %>% 
  separate_rows(value, sep = ",") %>% 
  separate(value, c("key", "value"), "=") %>% 
  mutate(across(c(key, value), str_squish))

knitr::kable(str)
```

`str_replace_all` to replace items in list of ingredients with names

```{r}
df <- df %>% 
  mutate(ingredients = str_replace_all(ingredients, c("Sa" = "salt",
                                                      "S\\*" = "non_sugar_sweetener",
                                                      "B" = "beans",
                                                      "S" =  "sugar",
                                                      "V" = "vanilla",
                                                      "L" = "lecithin",
                                                      "C" = "cocoa_butter"
                                                      )))

```


```{r}
library(recipes)
```

```{r}
df <- df %>% 
  separate(ingredients, into = c("ing_1",
                                 "ing_2",
                                 "ing_3",
                                 "ing_4",
                                 "ing_5",
                                 "ing_6"),
           sep = ",") 


```

```{r}
dummy_multi_choice_rec <- recipe(~ ., data = df) %>%
  step_dummy_multi_choice(starts_with("ing_")) %>%
  prep()

df <- bake(dummy_multi_choice_rec, new_data = NULL)
```


```{r}
# df %>% write_rds(here::here("data", "chocolate-bar-ratings-tidy.rds"))
```

