---
title: "Analyse"
author: "JJayes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r}
library(tidyverse)

theme_set(theme_light())

df <- read_rds(here::here("data", "chocolate-bar-ratings-tidy.rds"))
```

## Basic descrptives

What are the scores?

```{r}
df %>% 
  count(rating, sort = T)

df %>% 
  ggplot(aes(rating)) +
  geom_histogram(bins = 12)
```

Have they been increasing over time?

```{r}
df %>%
  ggplot(aes(review_date, rating, group = review_date)) +
  geom_jitter(alpha = .2) +
  geom_boxplot(varwidth = TRUE)
```

It looks like that while the average score has risen until 2010, there are consistently fewer low scoring bars.

```{r}
df %>%
  ggplot(aes(review_date, rating, group = review_date)) +
  geom_violin(aes(fill = review_date)) +
  geom_boxplot(width = .2) +
  scale_fill_viridis_c()
```

What about the different countries??

```{r}
df %>% 
  count(country_of_bean_origin, sort = T)

df %>% 
  add_count(country_of_bean_origin) %>% 
  filter(n > 60) %>% 
  group_by(country_of_bean_origin) %>% 
  summarise(mean_rating = mean(rating)) %>% 
  mutate(country_of_bean_origin = fct_reorder(country_of_bean_origin, mean_rating)) %>% 
  ggplot(aes(mean_rating, country_of_bean_origin)) +
  geom_col() +
  coord_cartesian(xlim = c(3,3.3))
```


```{r}
library(ggbeeswarm)

df %>% 
  add_count(country_of_bean_origin) %>% 
  filter(n > 60) %>% 
  group_by(country_of_bean_origin) %>% 
  mutate(country_of_bean_origin = fct_reorder(country_of_bean_origin, rating, .fun = mean)) %>% 
  ggplot(aes(rating, country_of_bean_origin)) +
  geom_quasirandom()
  
```

Cocoa percentage and score?

```{r}
df %>% 
  count(cocoa_percent, sort = T)

df %>% 
  ggplot(aes(cocoa_percent)) +
  geom_histogram(bins = 25)
```

70 percent is the most common

What about ingredients??

```{r}

df %>% 
  mutate(cocoa_percent = round(cocoa_percent, 1)) %>% 
  count(cocoa_percent, n_ingredients) %>% 
  ggplot(aes(cocoa_percent, n_ingredients, fill = n)) +
  geom_tile() +
  scale_fill_viridis_c() +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(x = "Cocoa percent",
       y = "Number of ingredients",
       fill = "Number of bars reviewed") +
  theme(legend.position = "bottom") +
  guides(fill = guide_colorbar(title.position = "bottom",
                               barwidth = 25,
                               title.hjust = .5))
```

Instead of 

```{r}
df %>% 
  mutate(cocoa_percent = round(cocoa_percent, 1)) %>% 
  ggplot(aes(cocoa_percent, n_ingredients, fill = rating)) +
  geom_tile() +
  scale_fill_viridis_c(option = "A") +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(x = "Cocoa percent",
       y = "Number of ingredients",
       fill = "Chocolate bar rating") +
  theme(legend.position = "bottom") +
  guides(fill = guide_colorbar(title.position = "bottom",
                               barwidth = 25,
                               title.hjust = .5))

```


## Correlation between ingredients

```{r}
library(corrr)

df %>%
  select(starts_with("ing_1")) %>%
  rename_with(.cols = everything(), ~ str_remove(.x, "ing_1_")) %>%
  correlate() %>%
  rearrange() %>%
  shave() %>%
  rplot(shape = 15, colours = c("midnightblue", "white", "darkorange")) 

df %>%
  select(starts_with("ing_1")) %>%
  rename_with(.cols = everything(), ~ str_remove(.x, "ing_1_")) %>% 
  correlate() %>% 
  network_plot()
```

TBC

```{r}
df %>%
  select(starts_with("ing_1")) %>%
  rename_with(.cols = everything(), ~ str_remove(.x, "ing_1_")) %>%
  correlate() %>%
  rearrange() %>%
  shave() %>%
  gt::gt()
```


## Word model

```{r}
df_characteristics <- df %>% 
  select(c(most_memorable_characteristics, rating)) %>% 
  separate_rows(most_memorable_characteristics, sep = ",") %>% 
  mutate(most_memorable_characteristics = str_squish(most_memorable_characteristics))
```

```{r}
df_characteristics %>% 
  count(most_memorable_characteristics, sort = T)
```

We can start with a naive analysis that looks only at average score per word

```{r}
df_characteristics %>% 
  group_by(most_memorable_characteristics) %>% 
  add_count() %>% 
  mutate(avg_rating = mean(rating)) %>% 
  ungroup() %>% 
  slice_max(avg_rating, n = 12, with_ties = F)

df_characteristics %>% 
  group_by(most_memorable_characteristics) %>% 
  add_count() %>% 
  filter(n > 3) %>% 
  mutate(avg_rating = mean(rating)) %>% 
  ungroup() %>% 
  distinct(most_memorable_characteristics, avg_rating) %>% 
  slice_max(avg_rating, n = 12, with_ties = F)
```


```{r}
library(tidymodels)
library(textrecipes)

df_characteristics_folds <- vfold_cv(df_characteristics)

glmnet_recipe <- 
  recipe(formula = rating ~ ., data = df_characteristics) %>% 
  step_tokenize(most_memorable_characteristics) %>% 
  step_tokenfilter(most_memorable_characteristics, max_tokens = 100) %>% 
  step_tf(most_memorable_characteristics) %>% 
  step_normalize(all_predictors(), -all_nominal()) 

glmnet_spec <- 
  linear_reg(penalty = tune(), mixture = 1) %>% 
  set_mode("regression") %>% 
  set_engine("glmnet") 

glmnet_workflow <- 
  workflow() %>% 
  add_recipe(glmnet_recipe) %>% 
  add_model(glmnet_spec) 

glmnet_grid <- tidyr::crossing(penalty = 10^seq(-6, -1, length.out = 20)) 

glmnet_tune <- 
  tune_grid(glmnet_workflow, df_characteristics_folds, grid = glmnet_grid)

glmnet_tune %>% 
  autoplot()

glmnet_model_final <- finalize_workflow(glmnet_workflow, glmnet_tune %>% 
  select_best())

final_fit <- glmnet_model_final %>% 
  fit(df_characteristics)
```


What does the fit look like?

```{r}
final_fit %>%
  extract_fit_parsnip() %>%
  tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(term = str_remove(term, "tf_most_memorable_characteristics_")) %>%
  mutate(sign = estimate > 0) %>%
  group_by(sign) %>%
  slice_max(estimate, n = 12) %>%
  ungroup() %>%
  filter(estimate != 0) %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(estimate, term, fill = sign)) +
  geom_col(show.legend = F) +
  geom_vline(xintercept = 0, lty = 2) +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "Effect of word on chocolate bar score",
       y = "Memorable characteristic")
```

